\chapter{Architecture and Design}

\section{Overview}

\section{Software architecture}

\subsection{Logical view}

Provide the software-architecture logical view for the major components as UML component diagram (or class diagram).

\subsection{Process view}

Provide the software-architecture process view for the major components as UML sequence diagram (or communication diagram).

\subsection{Physical view}
Provide the software-architecture physical view as UML deployment diagram.

\subsection{Details of each component in a \textbf{separate section}.}

\section{Software design}

\subsection{UML sequence/communication diagram}

Provide UML sequence/communication diagram for each use case scenario. You should show concurrent objects and the messages type (i.e. synchronous or asynchronous).


\subsection{Class diagram}
Provide class diagram to show classes’ relationship, internal classes data, and methods. This should be based on the use case scenarios, problem description, and use case scenarios sequence/communication diagrams.

\subsection{Normalization}

\subsubsection{1NF Normal Form}

\subsubsection{2NF Normal Form}

\subsubsection{3NF Normal Form}

\subsubsection{BCNF Normal Form}

\subsubsection{4NF Normal Form}

\subsection{ER diagram}

Provide the ER diagram for your data structure in the database (if any).

\subsection{State transition diagram}

Provide state transition diagram of the system and if needed for some components/classes

\section{User interface design}

Provide snapshots for the graphical user interface screens of the system.


