\chapter{Introduction}

This chapter comprises background of the project, the reasons for taking it, problems addressed by the project and expected outcomes. A good report starts with an introduction to the title of project. The necessary background information is provided to establish context of the project. The motivation and significance of the project should be highlighted. A crisp problem statement is followed by scope of the project along with any limitation or exclusions. The specific objectives to be achieved should be stated. A road-map or organization of report concludes the chapter.

\section{Overview}

In this section, you should write about the general review or summary of this project.

\section{Project Motivation}

In this section, you should write about the answer the following questions:

\begin{itemize}
\item Q1. What is the reasons behind your choice to develop this project?
\item Q2. Why your project is important?
\item Q3. What is the new idea that have been proposed by this project?
\end{itemize}


\section{Problem Statement}

write about the issues that have been addressed by this project and the conditions to be improved upon.

\section{Project Aim and Objectives}

Write about the overall purposes of this project, should be clearly and concisely defined. In this section you should answer the following questions:

\begin{itemize}
\item Q1. What is the goal that this project wants to achieve?
\item Q2. How this project can achieve this goal? 
\end{itemize}


\section{Project Scope}

Explains the boundaries (specified features and functions) of this project, 
establishes responsibilities for each team member and sets up procedures for how completed work will be verified and approved.

\section{Project Software and Hardware Requirements}

List the prerequisites software and hardware requirement of this project.

\section{Project Limitations}

you should clarify the limitations or parameters of the project and clearly identify any aspects that are not to be included.

\section{Project Expected Output}

Describe the desired results of the project.

\section{Project Schedule}

Listing of a project's milestones, activities, and deliverance's, with intended start and finish dates.

\section{Project, product, and schedule risks}

Describe the risk that the project takes longer than scheduled.

\section{Gantt Chart}

\subsection{Analyze and Requirement}

\subsection{Screen Design and Data Base}

\subsection{Algorithms Design}

\subsection{Testing}

\subsection{Document}

\subsection{Graph}